Query Optimization for Dynamic Imputation

### 2017-05-15 paper/algorithm.tex

This set $Q$ will be the Pareto frontier~\cite{pareto1964cours} of $S$, and it contains the best option for all feasible trade-offs of $\textsc{Time}$ and $\textsc{Penalty}$ for the current query. This
set of plans is significantly smaller than the set of all plans, which our algorithm prunes away.

@@

\textbf{Constructing $T$}:
As with $\textsc{Penalty}$, the time computation for \textit{Impute} depends on the properties of the underlying algorithm via a function $T$.
If we assume that the \textit{Impute} routine is CPU-bound, then we adjust $T$ by some constant factor $f$, thereby scaling the result to be comparable with IO-bound routines.

>>>>

This set $Q$ will be the Pareto frontier~\cite{pareto1964cours} of $S$, and it contains the best option for all feasible trade-offs of $\textsc{Time}$ and $\textsc{Penalty}$ for the current query. \review{This
set of plans is significantly smaller than the set of all plans, which our algorithm prunes away.}

@@

\textbf{Constructing $T$}:
As with $\textsc{Penalty}$, the time computation for \textit{Impute} depends on the properties of the underlying algorithm via a function $T$.
If we assume that the \textit{Impute} routine is CPU-bound, then we adjust $T$ by some constant factor $f$, thereby scaling the result to be comparable with I/O-bound routines.

### 2017-05-15 paper/relatedwork.tex

\review{
\textcite*{yang2015lenses} develop an incremental approach to ETL data cleaning, through the use
of probabilistic compositional repair operators called \textit{Lenses}. These can be used
to repair missing values by imposing data constraints such as \texttt{NOT NULL}. 
As with \ProjectName{}, they provide a way to balance the quality of the cleaning 
performed (expressed by the confidence of their output) and the cost of those operations. However, their 
repairs take place on a per-tuple basis, with the non-deterministic layer of their system replacing place-holder
variables with inferred values. In contrast, \ProjectName{} optimizes imputation at the plan-level and
provides the same impute technique for all tuples streaming through a given operator.
}

>>>>

\review{
\textcite*{yang2015lenses} develop an incremental approach to ETL data cleaning, through the use
of probabilistic compositional repair operators, called \emph{Lenses}, which balance quality of cleaning
and cost of those operations. These operators can be used
to repair missing values by imposing data constraints such as \texttt{NOT NULL}. However, the model
used to impute missing values must be pre-trained and all repairs are done on a per-tuple basis
rather than at the plan-level.
}
